---
title: "STAT 155 Final Data Analysis Project"
author: "Xi, Julia, Chenxin, Lian"
date: "12/18/2019 (Section 05)"
output:
  slidy_presentation: default
  ioslides_presentation: default
subtitle: A study of house age and house price in Taiwan
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r reading data into R, eval = TRUE, message=FALSE,echo=FALSE}
library("tidyverse")
data <- read_csv("RealEstate.csv")
```

```{r,message=FALSE,echo=FALSE}
dis <- data %>%
  select(distance)
distanceCat <- 0
distanceCat[dis <= 1500] <- "Walk"
distanceCat[dis > 1500 & dis <= 3000] <- "Bike"
distanceCat[dis > 3000] <- "Drive"
data <- data %>%
  mutate(distanceCat)
```

```{r,message=FALSE,echo=FALSE}
store <- data %>%
  select(store)
storeCat <- 0
storeCat[store == 0] <- "None"
storeCat[store > 0 & store <= 3] <- "Few"
storeCat[store > 3 & store <= 6] <- "Some"
storeCat[store > 6] <- "Many"
data <- data %>%
  mutate(storeCat)
```

```{r,message=FALSE,echo=FALSE}
lat <- data %>%
  select(latitude)
latitudeCat <- 0
latitudeCat[lat<=24.96] <- "Low"
latitudeCat[24.96<lat & lat<=24.98] <- "Medium"
latitudeCat[24.98<lat] <- "High"
data <- data %>%
  mutate(latitudeCat)
```

# Scientific background/motivation

*Research questions*

- Is house age associated with decreased house prices in Taiwan?

- Is house age associated with decreased house prices in Taiwan with latitude as a confounder?

- If there is an association between house age and decreased house-price, is this effect different when the distance to the nearest metro station varies with latitude as a confounder?

- Holding latitude constant, if there is an association between house age and decreased house-price, is this effect different when the number of convenience stores in the living circle varies?

## Description of study/data

- https://archive.ics.uci.edu/ml/datasets/Real+estate+valuation+data+set

- This data set was collected in Taiwan from 2012 to 2013 by Prof. I- Cheng Yeh and was used to build real estate valuation models in his paper (Yeh, I. C., & Hsu, T. K. (2018).

- The data include transaction date, house age (year), distance to the nearest metro station (meter), number of convenience stores in the living circle on foot, latitude (degree), longitude (degree), and house price of unit area (10000 New Taiwan Dollar per Ping, where 1 Ping = 3.3 meters squared).

```{r,echo=FALSE}
data %>%
    ggplot(aes(x = price)) +
    geom_histogram(fill = "steelblue") +
    xlab('House price of unit area(10000 New Taiwan Dollar per Ping)') +
    ylab('Counts') +
    theme_minimal()
```

```{r,echo=FALSE}
data %>%
    ggplot(aes(x = age)) +
    geom_histogram(fill = "steelblue") +
    xlab('The house age(year) ') +
    ylab('Counts') +
    theme_minimal()
```

# Question 1
Is house age associated with decreased house prices in Taiwan?

Graph

```{r, echo = FALSE}
data %>%
  ggplot(aes(x = age, y = price)) +
  geom_point(color = 'steelblue') + 
  geom_smooth(method = 'lm', se = FALSE) +
  xlab('House age (year)') + 
  ylab('House price of unit area(10000 New Taiwan Dollar per Ping') +
  theme_minimal()
```

Regression Model

```{r, echo = FALSE}
lm(price ~ age, data = data)  %>% 
  summary()

lm(price ~ age, data = data) %>%
  confint()
```

# Question 2
Is house age associated with decreased house prices in Taiwan with latitude as a confounder?

Graph

```{r,echo=FALSE}
data %>%
  ggplot(aes(x = age, y = price, color = latitudeCat)) + 
  geom_point() +
  geom_smooth(method = 'lm', se = FALSE) +
  xlab('House age (year)') + 
  ylab('House price of unit area(10000 New Taiwan Dollar per Ping') +
  theme_minimal()
```

Regression Model

```{r,echo=FALSE}
lm(price ~ age+latitude,  data = data)  %>% 
  summary()

lm(price ~ age+latitude,  data = data) %>%
  confint()
```

# Research question 3&4

Holding latitude constant, if there is an association between house age and decreased house-price, is this effect different when the distance to the nearest metro station varies?

```{r,echo=FALSE}
data %>%
  ggplot(aes(x = age, y = price, color = distanceCat)) + 
  geom_point() +
  geom_smooth(method = 'lm', se = FALSE) +
  xlab('House age (year)') + 
  ylab('House price of unit area(10000 New Taiwan Dollar per Ping') +
  theme_minimal()
```

```{r,echo=FALSE}
lm(price ~ age+latitude+distance+age:distance,  data = data) %>% 
  summary()

lm(price ~ age+latitude+distance+age:distance,  data = data) %>%
  confint()
```

Holding latitude constant, if there is an association between house age and decreased house-price, is this effect different when the number of convenience stores in the living circle varies?

```{r,echo=FALSE}
data %>%
  ggplot(aes(x = age, y = price, color = storeCat)) + 
  geom_point() +
  geom_smooth(method = 'lm', se = FALSE) +
  xlab('House age (year)') + 
  ylab('House price of unit area(10000 New Taiwan Dollar per Ping') +
  theme_minimal()
```

```{r,echo=FALSE}
lm(price ~ age+latitude+store+age:store,  data = data)  %>% 
  summary()

lm(price ~ age+latitude+store+age:store,  data = data) %>%
  confint()
```

# Discussion

- summary of what you found
1. Is house age associated with decreased house prices in Taiwan?
The house age has a negative linear relationship associated with house prices in Taiwan.

2. Is house age associated with decreased house prices in Taiwan with latitude as a confounder? 
The house age has a negative linear relationship associated with house prices in Taiwan with latitude as a confounder.

3. If there is an association between house age and decreased house-price, is this effect different when the distance to the nearest metro station varies with latitude as a confounder? 
If there is an association between house age and decreased house-price, this effect is different when the distance to the nearest metro station varies with latitude as a confounder.

4. If there is an association between house age and decreased house-price, is this effect different when the number of convenience stores in the living circle varies with latitude as a confounder? 
If there is an association between house age and decreased house-price, there is not significant evidence showing that the number of convenience stores in the living circle is an effect modifier.

- tell us about anything you found challenging, or unique features of your data that you had to deal with (and how you dealt with those features)
Our original data are all quantitative. However, we categorize these data and make our predictors categorical. In this way, we feel that we could have a more meaningful result.

- discuss any limitations of your data or analyses
We subjectively categorized our data. However, these categories might not applied to everyone. For instance, we decided that the Walking Distance is 0-1500 meters (which is about 1 mile) and Biking Distance is 1500-3000 meters. However, not everyone will agree with this categorization.

- suggest areas for improvement and/or future work
Figure out a standard that most people will agree with to categorize the data.
If there are other data sets are similar to this data set, the same models could be used to test whether there will be similar results. 